%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{setspace}
\usepackage{dsfont}
\usepackage[shortlabels]{enumitem}
\usepackage{url}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[authoryear,round]{natbib}
\usepackage[colorlinks = true, linkcolor = blue, citecolor = blue, citecolor = blue]{hyperref}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{indentfirst}
\usepackage{setspace}
\usepackage{soul}
\usepackage[normalem]{ulem}

\usetikzlibrary{automata,arrows,positioning,calc}
\usetikzlibrary{plotmarks}

\addtolength{\voffset}{-1.5cm} \addtolength{\hoffset}{-1cm}
\addtolength{\textwidth}{2.5cm} \addtolength{\textheight}{2.5cm}


\pgfplotsset{compat=1.17}
\renewcommand{\baselinestretch}{1.5}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
\textbf{ \Large Instructions for the Experiment}
\end{center}


Welcome to our study. At this time, please make sure you have turned off and put away all personal electronic devices. This study will take no more than 75 minutes. You will be paid your earnings from each part of the study in addition to the \$7.50 participation payment in cash. Your earnings will depend on the decisions you and others make in this study, so it is important that you fully understand these instructions. These earnings will be denominated in experimental currency units (or ECUs for short).  At the end of the study, ECUs will be converted into dollars at the exchange rate of 10 ECUs for 1 dollar and will be paid to you privately in cash.   If you have a question at any point, please raise your hand. 

\newpage
 
    


\subsection*{Page 1}

You will interact with other participants in this session through a computer program. Your personal identifying information will not be revealed to anyone. To the participants that you will interact with, you will be referred to as a unique alphabet randomly assigned to you.  For this session, you will be referred to as 
    \begin{center}
        ``Participant \underline{~~~~~}.''
    \end{center} 

\vspace{0.2in}
    
This study consists of 4 \textbf{segments}. At the beginning of these segments, all participants will be randomly placed in a group of 4. Each group will remain the same throughout a segment. When a new segment begins, all participants will be randomly placed in a new group of 4. In these 4 segments, you will be placed in 4 different groups and will not interact with the same persons in different segments.

\newpage


\subsection*{Page 2}


  Each segment consists of an uncertain number of \textbf{periods}. The number of periods in a segment is determined as follows: 
\begin{itemize}
    \item For each period, the computer has randomly selected a number from 1 to 5, each with a 20\% chance, for the entire session to determine whether another period of the same segment will follow. 
    \item 	If the selected number is from 1 to 4, the next period will follow. If the selected number is 5, the segment will end.
    \item 	We will reveal the selected number to you at the end of each period. So, at the beginning of each period, you only know that there is an 80\% chance that another period of the same segment will follow and there is a 20\% chance that the segment will end after this period. 
\end{itemize}


\newpage


\subsection*{Page 3 }


Each period consists of 2 \textbf{stages}.

\vspace{0.2in}

In stage 1, you will have a chance to communicate with other participants in your group through a chat box. For period 1 of each stage you will have 2 minutes (or 120 seconds) to chat. In each of the subsequent periods, you will have only 30 seconds to chat.

\vspace{0.2in}

You can chat about any topic but please avoid  profanities and offensive language. These will not be tolerated.  Do not use any language other than English. Also, avoid revealing your current seating location or personal identifying information about yourself such as your name, age, major, gender, etc. 

\vspace{0.2in}
    
It is important that we practice this feature before the study begins.  On the bottom of the screen you see a text field. You are now randomly matched with 3 other participants in this session. You will not be matched with these participants again in the study. Try to send them messages. Once you are familiar with the chat box, please click the ``Continue'' button.
    
 

\newpage


\subsection*{Page 4}

In stage 2, you will will face a decision task described below.
    

\begin{itemize}
    \item Each participant is endowed with 25 tokens and has to allocate these tokens between a \textbf{Private Account} and a \textbf{Group Account}. Each participant has their own Private Account and there is only one Group Account for each group.
    
    \item You will earn 1.0 ECU for each token you allocate to your Private Account. Each token allocated to the Group Account of your group yields a return of 1.6 ECUs. Everyone in the group will receive an equal share of earnings from the Group Account. Since there are 4 participants in a group, each participant will receive 
    \begin{center}
        $\frac{1}{4} \times 1.6 \times $ the total number of tokens in the Group Account
    \end{center}
    in ECUs regardless of the number of tokens each has allocated to the Group Account.

     \item We would like to emphasize each participant in a group will receive the same amount of ECUs from the Group Account, even though they allocated a different number of tokens to the Group Account.
    
\end{itemize}



\newpage

\subsection*{Page 5}

Consider the following examples.


\begin{itemize}
    \item If each participant in a group allocates 0 tokens to the Group Account, then the Group Account will have 0 tokens. Each participant will earn 25 ECUs from their Private account and 0 ECUs from their Group Account. The total earnings for the period will be 25 ECUs for each participant in the group.

    \item If each participant in a group allocates 25 tokens to the Group Account, then the Group Account will have $4 \times 25 =100$ tokens. Each participant will earn 0 ECUs from their Private account and $\frac{1}{4} \times 1.6 \times 100 = 40$ ECUs from their Group Account. The total earnings for the period will be 40 ECUs for each participant in the group.

\end{itemize}

Now you have a chance to make some practice decisions. By practicing, you will become familiar with how your earnings are determined. You will not interact with other participants during this practice, and your practice decisions will not be shown to anyone. You will not earn anything for practice decisions.

\vspace{0.2in}

Just like in the decision tasks of this study, you will practice allocating ECUs between your Private Account and the Group Account. During these practice decisions, you will also choose hypothetical allocations for the three other participants in your group. Try different allocations for all four participants and click the ``calculate'' button to see each participant's earnings. In the actual tasks, you will be matched with three human participants who will make their own allocation decisions.


\newpage



\subsection*{Page 6}


Even though you will make decisions in many periods and the computer will calculate your earnings in ECUs for all of these periods, the computer will randomly select \underline{\textbf{only 1 segment}} to calculate your cash payment. The computer will use the sum of your earnings from all periods in the selected segment and convert it into dollars at the exchange rate of 10 ECUs for 1 dollar. You will know which segment is selected for your cash earnings at the end of the study.


\newpage


\subsection*{Page 7}

Before you proceed to segment 1, please answer the following quiz questions to make sure you fully understand the instructions. Your quiz answers will not affect your earnings from this part. If an answer is wrong and you do not understand why it is wrong, please raise your hand.


\begin{enumerate}
    \item How many participants are in a group?  \underline{~~~~~~}
    
    \item How many segments are in this study?  \underline{~~~~~~}

    \item The number of periods in each segment in uncertain. True/False 

    \item During each period, the probability that it is the last period of the segment is 80\%. True/False 

    \item Between any two segments, other participants assigned to your group will be different. True/False 
  
    \item Between any two periods of the same segment, other participants assigned to your group will be different. True/False 

    \item In stage 2 of each period, each participant is endowed with \underline{~~~~~~} tokens.

    \item If each participant in a group allocates 10 tokens to the Group Account, each participant's earnings will be \underline{~~~~~~} ECUs.

    \item If you allocate 25 tokens to your Group Account while all other participants in you group allocate zero tokens to your Group Account, your earnings will be \underline{~~~~~~} ECUs.

    \item Your cash earnings from the study is the sum of the ECUs that you earn in all segments. True/False 

\end{enumerate}

\newpage 

\subsection*{Page 8}

You have submitted all your decisions for this study.  Please answer the following survey questions. Your answers will not affect your earnings from this study.


\begin{enumerate}
    \item Your gender:  
    \begin{itemize}
        \item Male
        \item Female
        \item Prefer not to answer
    \end{itemize}

    \item Your ethnicity:
    \begin{itemize}
        \item White or Caucasian
        \item Black or African American
        \item Hispanic or Latino/a/x
        \item Asian or Asian American
        \item Multiracial
        \item Other (Please specify) \underline{~~~~~~}
        \item Prefer not to answer
    \end{itemize}

    \item Your age:  \underline{~~~~~~}

    \item Your major(s): \underline{~~~~~~}

    \item How many siblings did you have growing up? \underline{~~~~~~}

    \item How important is religion in our daily life?
       \begin{itemize}
        \item Not at all importaint
        \item Slightly important
        \item Important
        \item Fairly important
        \item Very important
    \end{itemize}
    
\end{enumerate}


\end{document}