%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{setspace}
\usepackage{dsfont}
\usepackage[shortlabels]{enumitem}
\usepackage{url}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[authoryear,round]{natbib}
\usepackage[colorlinks = true, linkcolor = blue, citecolor = blue, citecolor = blue]{hyperref}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{indentfirst}
\usepackage{setspace}
\usepackage{soul}
\usepackage[normalem]{ulem}

\usetikzlibrary{automata,arrows,positioning,calc}
\usetikzlibrary{plotmarks}

\addtolength{\voffset}{-1.5cm} \addtolength{\hoffset}{-1cm}
\addtolength{\textwidth}{2.5cm} \addtolength{\textheight}{2.5cm}


\pgfplotsset{compat=1.17}
\renewcommand{\baselinestretch}{1.5}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
\textbf{ \Large Instructions for the Experiment}
\end{center}

\section{Welcome}

Welcome to our study. At this time, please make sure you have turned off and put away all
personal electronic devices. This study will take no more than 75 minutes. You will be paid your
earnings from each part of the study in addition to the \$7.50 participation payment in cash. Your earnings will depend on the decisions you and others make in this study, so it is important that you fully understand these instructions. These earnings will be denominated in experimental currency units (or ECUs for short). At the end of the study, ECUs will be converted into dollars at the exchange rate of 10 ECUs for 1 dollar and will be paid to you privately in cash. If you have a question at any point, please raise your hand.


\section{Structure}


You will interact with other participants in this session through a computer program. Your
personal identifying information will not be revealed to anyone. To the participants that you will interact with, you will be referred to as a unique alphabet \textbf{letter} randomly assigned to you. For this session, you will be referred to as

\begin{center}
``Participant [insert label (A-R)]''
\end{center}

This study consists of 4 segments. At the beginning of these segments, all participants will be
randomly placed in a group of 4. Each group will remain the same throughout a segment. When
a new segment begins, all participants will be randomly placed in a new group of 4. In these 4
segments, you will be placed in 4 different groups and will not interact with the same persons in
different segments.


\section{Ending of Segments}

Each segment consists of an uncertain number of rounds. The number of rounds in a segment is
determined as follows:

\begin{itemize}
    \item For each round, the computer has randomly selected a number from 1 to 5, each with a 20\% chance, for the entire session to determine whether another round of the same segment will follow.
    \item If the selected number is from 1 to 4, the next round will follow. If the selected number is 5, the segment will end.
    \item We will reveal the selected number to you at the end of each period. So, at the beginning of each round, you only know that there is an 80\% chance that another round of the same segment will follow and there is a 20\% chance that the segment will end after this round.
\end{itemize}



\section{Tokens/Points and allocation}

\begin{itemize}
    \item Each participant is endowed with 25 tokens/points at the beginning of each round and has to allocate these tokens/points between a Private Account and a Group Account. Each participant has their own Private Account and there is only one Group Account for each group. 
    \item You will earn 1.0 ECU for each token/point you allocate to your Private Account. Each token/point allocated to the Group Account of your group yields a return of 1.6 ECUs. Everyone in the group will receive an equal share of earnings from the Group Account. Since there are 4 participants in a group, each participant will receive

\begin{center}
$\frac{1}{4} \times 1.6 \times $ the total number of tokens/points in the Group Account
\end{center}

in ECUs. \sout{regardless of the number of tokens each has allocated to the Group Account}
    \item We would like to emphasize each participant in a group will receive the same amount of ECUs from the Group Account, even though they allocated a different number of tokens/points to the Group Account.
\end{itemize}



\section{Decisions}
Each round consists of 2 stages.
\begin{itemize}
    \item In stage 1, you will choose your allocation to the group
account \textbf{(a whole number from 0 to 25)}.  
    \item For stage 2, you will view the results of the round and chat with your group
members. 
    \item You will be able to see  \textbf{the total number of tokens/points in the Group Account and} each group member's allocation. [For Treatment 2:  You will be able to see the total number of tokens/points in the Group Account, but not each group member's allocation.]
    \item You will be able to chat with your group members for \textbf{60 seconds-must decide on this}. You can chat about any topic but please avoid profanities and offensive language. These will not be tolerated. Do not use any language other than English. Also, avoid revealing your current seating location or personal identifying information about yourself such as your name, age, major, gender, etc. Even though you will make decisions in many rounds and the computer will calculate your earnings in ECUs for all of these rounds, the computer will randomly select only 1 segment to calculate your cash payment. The computer will use the sum of your earnings from all rounds in the selected segment and convert it into dollars at the exchange rate of 10 ECUs for 1 dollar. You will know which segment is selected for your cash earnings at the end of the study.
\end{itemize}


[They can chat before knowing that the period is the last one of the segment right?]


\section{Practice}
Use this page to practice your allocation to the Group Account...

[Payoff calculator interface with inputs for your allocation and 3 other group members'
allocations]


Remember that this is a practice round. You are not interacting with other players. In actual
rounds, you will interact with other players and you will not know the other group member
allocations until after you submit your own allocation.


[Please add 25 - (15 for example) = 10 for the private account, and remove hypothetical]

\section{Quiz}
Before proceeding, please complete the quiz. \textbf{You are allowed to use the payoff calculator to help you answer the following quiz questions}.

\begin{enumerate}
\item How many participants are in a group? (Multiple Choice)

4

\item  How many segments are in this study? (Multiple Choice)

4

\item  The number of rounds in each segment is uncertain. (True/False)

True

\item  During each round, the probability that it is the last round is 80\%. (True/False)

False (the probability that it is the last round is 20\%)

\item  Between segments, your group members change. (True/False)

True

\item  Between rounds of the same segment, your group members change. (True/False)

False  (Between rounds of the same segment, your group members do not change)

\item  Each participant starts with how many tokens/points per round? (Multiple Choice)

25

\item  If \textbf{everyone in the group} allocates 10 tokens to the Group Account, \sout{each earns how many ECUs} each member's earnings are? (Multiple Choice)

31 (15 from the Private Account and 16 from the Group Account)


\item  If you allocate 25 tokens and others allocate 0, your earnings are? (Multiple Choice)

10 (0 from the Private Account and 10 from the Group Account)

\item  If you allocate 0 tokens and \textbf{each of other members} allocates 25, your earnings are? (Multiple Choice)

55 (25 from the Private Account and 30 from the Group Account)

\item  Your \textbf{total} earnings are the sum of ECUs from all segments. (True/False)

False (Your total earnings are the sum of ECUs from only one randomly selected segment.)

[provide all answers after 2 minutes]


\end{enumerate}

\end{document}